final_project_draft

### 2022-03-30 draft.Rmd
March 30 graded after class commit. Created a few simple visualizations.

## Political Donations
```{r}
library(tidyverse)
library(ggthemes)
pol_donations <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/sports-political-donations.csv")
pol_donations <- pol_donations %>% rename(year = 'Election Year')
```

```{r}
pol_donations 
nfl <- pol_donations %>% filter(League == "NFL") 
nfl %>% group_by(Party) %>%
  summarise(n = n())
```

```{r, message = FALSE, warning = FALSE, echo = FALSE}
owner_rank <- pol_donations %>% group_by(Owner) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(desc(n))) %>%
  filter(rank <= 25) %>%
  mutate(owner = fct_reorder(.f = Owner, .x = n))

ggplot(data = owner_rank, aes(x = owner, y = n)) +
  geom_point(size=5, color="red", fill=alpha("orange", 0.3), alpha=0.7, shape=21, stroke=2) +
  geom_segment(aes(x = owner, xend = owner, y = 0, yend = n)) +
  coord_flip() +
    labs(title = "Most Frequent Donators Among All Leagues",
       y = "Count",
       x = "Owners") +
  theme_fivethirtyeight() 
```

## Blockbusters
```{r}
library(tidyverse)
blockbusters <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/Blockbusters_2019-1977.csv")
blockbusters

ggplot(data = blockbusters, aes(x = release_year, y = length_in_min)) +
  geom_line()
```

## History of Rock
```{r}
library(tidyverse)
history_of_rock <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/history-of-rock-spotify.csv")

history_of_rock %>%

led <- history_of_rock %>% filter(artist == "Led Zeppelin")

ggplot(data = led, aes(x = release_date, y = popularity)) +
  geom_line() 
```

## Unemployment

```{r}
unemployment_data_us <- read_csv("data/unemployment_data_us.csv")
unemployment_data_us
```

>>>>

## Political Donations of Professional Sports Team Owners 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(tidyverse)
library(ggthemes)

pol_donations <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/sports-political-donations.csv")

pol_donations <- pol_donations %>% rename(year = 'Election Year') %>% mutate(amount = parse_number(Amount)) %>% 
  mutate(Recipient = fct_recode(Recipient, Hillary_Victory_Fund = "HILLARY VICTORY FUND", 
                                Hillary_Victory_Fund = "Hillary Victory Fund",
                                Office_Of_Commissioner_of_MLB_PAC = "Office of the Commissioner of Major League Baseball PAC",
                                Office_Of_Commissioner_of_MLB_PAC = "OFFICE OF THE COMMISSIONER OF MAJOR LEAGUE BASEBALL POLITICAL ACTION COMMITTEE"))

library(plotly)
```

## Top 25 Highest Political Donations by NFL Team Owners in 2016 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
high_donations <- pol_donations %>% filter(year == "2016" & League == "NFL") %>%
  mutate(amount = parse_number(Amount)) %>%
  arrange(desc(amount)) %>%
  mutate(Rank = rank(desc(amount))) %>%
  filter(Rank <= 25) %>%
  mutate(owner_ordered = fct_reorder(.f = Owner, .x = amount)) %>%
  mutate(party = fct_relevel(Party, c("Republican", "Democrat", "Bipartisan")))

plot1 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = " ", 
       y = " ",
       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
       colour = "Political Party",
       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
  scale_colour_viridis_d()

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = " ", 
       y = " ",
       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
       colour = "Political Party",
       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
  scale_colour_viridis_d()

    scale_x_discrete("Amount Donated", labels = abbreviate)

scale_x_discrete(breaks = c("0e+00", "1e+05", "2e+05", "3e+05", "4e+05"),
                  labels = c("0", "100", "200", "300", "400"))

ggplotly(plot1, tooltip = "label") 
```

## Owners Who Donate The Most Frequently and How Much 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
owner_rank <- pol_donations %>% group_by(Owner, League) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

frequent <- pol_donations %>% group_by(Owner) %>%
  mutate(n = n()) %>%
  filter(n >= 65) %>%
  arrange(desc(n)) %>%
  mutate(donations = as.numeric(n))

ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = League)) +
  geom_point() +
  labs(title = "Owners Who Have Made the Most Donations",
       y = "Owners",
       x = "Amount Donated",
       colour = "League") +
  theme_hc() +
  scale_colour_viridis_d()

plot2 <- ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = League)) +
  geom_point() +
  labs(title = "Owners Who Have Made the Most Donations",
       y = "Owners",
       x = "Amount Donated",
       colour = "League") +
  theme_hc() +
  scale_colour_viridis_d()

ggplotly(plot2, tooltip = "label")

test <- frequent %>% mutate(owner = fct_reorder(.f = Owner, .x = n))
test2 <- frequent %>% mutate(owner = fct_inorder(Owner))
```

## Going off Second Political Donations Visualization
```{r}
library(knitr)
library(pander)
library(tidyverse)

owner_rank2 <- pol_donations %>% group_by(Owner, Team) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  filter(n >= 65)

kable(owner_rank2, caption = "Frequency of Donations from 2016 to 2020",
      col.names = c("Owner", "Team", "Amount of Donations Made"))
```

## Examining Top Donator 
```{r}
library(ggthemes)
charles_johnson <- pol_donations %>% filter(Owner == "Charles Johnson") %>%
  filter(year == 2016 | year == 2018 | year == 2020)

cj_party <- charles_johnson %>% group_by(Party) %>%
  summarise(n = n()) %>%
  mutate(party = fct_reorder(.f = Party, .x = n)) %>%
  mutate(Party = fct_relevel(party, c("Republican", "Bipartisan, but mostly Republican",
                                        "Democrat")))

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d() +
  labs(title = "Count of Donations",
       x = "Political Party",
       y = "Count") +
  theme_hc()
```

```{r}
owner_rank2
```

## Organizations Receiving Most Donations Across All Leagues
```{r}
recipients <- pol_donations %>% group_by(Recipient, Party) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  filter(n >= 15) %>%
  ungroup() %>%
  mutate(recipient = fct_reorder(.f = Recipient, .x = n)) %>%
  mutate(Party = fct_relevel(Party, c("Bipartisan", "Republican", "Democrat")))

ggplot(data = recipients, aes(x = recipient, y = n, colour = Party)) +
  geom_point() +
  geom_segment(aes(x = recipient, xend = recipient, y = 0, yend = n)) +
  coord_flip() +
  labs(x = "Recipients",
       y = "Count") +
  labs(title = "Organizations Receiving Most Donations Across All Leagues") +
  theme_hc() +
  scale_colour_brewer(palette = "Dark2")
```

## Blockbusters
```{r, message = FALSE, warning = FALSE, echo = FALSE}
blockbusters <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/Blockbusters_2019-1977.csv")
blockbusters
```

## Blockbuster Ratings: 1977 to 2019
```{r, message = FALSE, warning = FALSE, echo = FALSE}
blockbusters %>% group_by(mpaa_rating) %>%
  summarise(n = n())

blockbusters1 <- blockbusters %>% filter(!is.na(mpaa_rating)) %>%
  rename(Film = 'film_title')

plot6 <- ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating,
                                          label = Film)) +
  geom_point() +
  labs(y = "IMDB Rating",
       x = "Release Year",
       colour = "MPAA Rating",
       title = "Blockbuster Ratings: 1977 to 2019") +
  theme_hc() +
  scale_colour_brewer(palette = "Dark2")

ggplotly(plot6, tooltip = "label")
```

## 
```{r}
blockbusters

interest <- blockbusters %>% mutate(rank = rank(desc(imdb_rating))) %>%
  select(rank, everything()) %>%
  arrange(rank) %>%
  slice(1:5) %>%
  mutate(film_title = fct_recode(film_title, 
                                 LOTR_The_Return_Of_The_King = "The Lord of the Rings: The Return of the King",
                                 LOTR_Fellowship_Of_The_Ring = "The Lord of the Rings: The Fellowship of the Ring"))
interest

interest2 <- blockbusters %>% mutate(rank = rank(imdb_rating)) %>%
  select(rank, everything()) %>%
  arrange(rank) %>%
  slice(1:5)
interest2

library(ggrepel)
ggplot(data = interest, aes(x = release_year, y = domestic_gross)) +
  geom_point() +
  geom_label_repel(data = interest, aes(label = film_title)) +
  geom_point(data = interest2, aes(x = release_year, y = domestic_gross)) +
  geom_label_repel(data = interest2, aes(label = film_title))

ggplot(data = blockbusters, aes(x = release_year, y = film_budget)) +
  geom_hex() +
  labs(x = "Release Year",
       y = "Film Budget") 
```

## History of Rock
```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(tidyverse)
history_of_rock <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/history-of-rock-spotify.csv")
history_of_rock
```

## Most Popular Nirvana Songs 
```{r}
history_of_rock %>% group_by(artist) %>%
  summarise(n = n()) %>% arrange(desc(n))

nirvana <- history_of_rock %>% rename(Popularity = 'popularity') %>%
  filter(artist == "Nirvana") %>% arrange(desc(Popularity)) %>%
  mutate(order = fct_reorder(.f = name, .x = Popularity)) %>%
  rename(Release_Date = 'release_date')

nirvana %>% select(order, everything())

plot3 <- ggplot(data = nirvana, aes(x = order, y = Popularity, label = Popularity, colour = Popularity)) +
  geom_point() +
  geom_segment(aes(x = order, xend = order, y = 0, yend = Popularity)) +
  coord_flip() +
  labs(title = "Most Popular Nirvana Songs",
       colour = "Popularity", 
       x = " ",
       y = " ") +
  theme_hc() +
  scale_colour_viridis_b()

ggplotly(plot3, tooltip = "label")
```

```{r}
beatles <- history_of_rock %>% filter(artist == "The Beatles")

plot10 <- ggplot(data = beatles, aes(x = release_date, y = popularity)) +
  geom_line() +
  geom_point() +
  labs(x = "Release Date",
       y = "Popularity")

ggplotly(plot10, tooltip = "label")

beatles %>% arrange(desc(popularity)) 
```

## Unemployment Data Set
```{r}
library(lubridate)
unemployment <- read_csv("data/unemployment_data_us.csv")
ggplot(data = unemployment, aes(x = Date, y = Professional_Degree)) +
  geom_point()
```
